Supermassive black hole and host bulge affairs \\ I. True to life galaxy decomposition.

### 2015-06-02 papers/data_paper/datapaper.tex
onedayleft

@@

  inner component?? ok fuck it

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3079.}
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3377.}
  \end{center}
  \end{figure}

>>>>

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n1374_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 1374.
  NGC 1374 is an elliptical galaxy. 
  A Gaussian function in our model accounts for a relatively faint nuclear component. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 1374.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + G-n & $25.6$  &  $3.7$ \\
  T.W. 1D eq.  & S-bul + G-n & $24.8$  &  $4.1$ \\
  T.W. 2D      & S-bul + m-n & $25.2$  &  $3.7$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n1374}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3079_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3079.
  NGC3079 is an edge-on, late-type barred spiral galaxy 
  with a Seyfert AGN \citep{veroncettyveron2006} and circumnuclear dust \citep{martini2003}. 
  The bar extends out to $R_{\rm maj} \lesssim 70''$. 
  We truncate the light profile at $R_{\rm maj} \sim 65''$, before the ``edge'' of the bar, 
  and we model the combination of the disk and the bar with a Ferrer function. 
  A Gaussian function accounts for the AGN emission. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 2974.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + F-(bar+d) + G-n  & $6.8$  &  $1.3$ \\
  T.W. 1D eq.  & S-bul + F-(bar+d) + G-n  & $4.3$  &  $1.1$ \\
  \hline
  S+11         & S-bul + e-d + G-bar + G-n & $74.1$  &  $2.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n2974}
  \tablecomments{
  It is not clear why S+11 obtained a dramatically larger bulge effective radius. 
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
  \caption{Best-fit model and isophotal parameters for NGC 3377.
  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3384.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  T.W. 1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
  T.W. 1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
  T.W. 2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
  \hline
  GD07         & S-bul     		     & $44.1$  &  $3.0$ \\
  S+11         & S-bul     		     & $55.2$  &  $6.0$ \\
  B+12         & S-bul     		     & $43.5$  &  $3.5$ \\
  L+14         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3384}
  \end{table}

  The morphology of NGC3377 is similar to NGC0821. 
  The unsharp mask reveals an embedded disc and the extended velocity field confirms that 
  it is not a large-scale disc. 
  The residual image from a 2D single S\'ersic fit diplays the unsubtracted embedded disc
  and an additional nuclear ($\lesssim 10''$) component.
  The embedded disc is very close to edge-on.
  In the 2D fit we adopt a S\'ersic + edge-on disc model, after masking the third nuclear component. 
  In the 1D fit we are not able to model the embedded disc with an exponential function, 
  probably because of the orientation of the disc. 
  The best results are obtained when a Ferrer function is employed. 
  We tried to model the nuclear cusp with a PSF or a gaussian function. The gaussian function parameters
  resulted highly degenerate with the Ferrer function parameters, leading us to prefer a PSF profile. \\
